`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`

### 2020-07-23 analysis/VOCC/3-vocc-dist.Rmd
dvocc calc based on med

---
title: "`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    # species: "Redbanded Rockfish"
    # species: "Widow Rockfish"
    # species: "Canary Rockfish"
    # species: "English Sole"
    # species: "Dover Sole"
    # species: "Flathead Sole"
    # species: "Sablefish"
    species: "Arrowtooth Flounder"
    immature: T
    region: "West Coast Vancouver Island"
    # region: "both odd year surveys"
    # region: "West Coast Haida Gwaii"
    covs: "-tv-depth-only"
    climate_mod: "2020-06-20-more2016"
    scrambled_years: FALSE
---

@@

# Calculate climate velocity
### Temperature
```{r}
rm(gf2)
try({gf2 <- readRDS(paste0("data/_climate_vocc/temp-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
})

@@

# FULL DATASET
# mean(gf2$sd, na.rm = T) # [1] 0.3434
# min(gf2$sd, na.rm = T) # [1] 0.1266
# max(gf2$sd, na.rm = T) # [1] 1.12
# median(gf2$sd, na.rm = T) # [1] 0.287
# 
# 2008 DATASET
mean(gf2$sd, na.rm = T) # [1] 0.3274
temp_min_sd <- min(gf2$sd, na.rm = T) # [1] 0.1035
max(gf2$sd, na.rm = T) # [1] 1.248
temp_median_sd <- median(gf2$sd, na.rm = T) # [1] 0.2882

temp_sd_choice <- temp_min_sd
lower_change_t <- temp_sd_choice*2
upper_change_t <- temp_sd_choice*2

@@

saveRDS(gf2, file = paste0("data/_climate_vocc/temp-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
}

# mean(gf2$sd, na.rm = T) # [1] 0.3274
temp_min_sd <- min(gf2$sd, na.rm = T) # [1] 0.1035
# max(gf2$sd, na.rm = T) # [1] 1.248
temp_median_sd <- median(gf2$sd, na.rm = T) # [1] 0.2882

# temp_sd_choice <- temp_min_sd
# lower_change_t <- temp_sd_choice*2
# upper_change_t <- temp_sd_choice*2
```

@@

### Dissolved Oxygen
```{r }

rm(gf0)
try({gf0 <- readRDS(paste0("data/_climate_vocc/DO-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
})

@@

do_sd_choice <- do_median_sd

lower_change_d <- c(do_sd_choice*2) 
upper_change_d <- c(do_sd_choice*2)

@@

lower_change_td <- c(Inf, do_sd_choice*2) 
upper_change_td <- c(temp_sd_choice*2, do_sd_choice*2)

@@

gf0 <- left_join(gf0, dv_td)

saveRDS(gf0, file = paste0("data/_climate_vocc/DO-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
}

do_min_sd <- min(gf0$sd, na.rm = T)
do_median_sd <- median(gf0$sd, na.rm = T)
do_sd_choice <- do_median_sd
```

### BIOTIC VECTORS
```{r}
gf3 <- vocc_gradient_calc(d, "est",
  scale_fac = scale_fac,
  indices = indices,
  # divisor = 1, #default of 10 gives per decade
  log_space = TRUE,
  quantile_cutoff = 0.025
)

@@

```{r eval=T}
plot_vocc(vocc_t,
    raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "temp_dvocc",
  fill_label = "temperature \nkm/decade",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
   # viridis_option = "C",
   mid_fill = "lightyellow",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
    title = "distance-based temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year), " min temp SD = ", temp_min_sd, " x 2 for 95% min threshold of change")
)
```

>>>>

---
title: "`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    # species: "Redbanded Rockfish"
    # species: "Widow Rockfish"
    # species: "Canary Rockfish"
    # species: "English Sole"
    # species: "Dover Sole"
    # species: "Flathead Sole"
    # species: "Sablefish"
    species: "Arrowtooth Flounder"
    immature: T
    # region: "West Coast Vancouver Island"
    region: "both odd year surveys"
    # region: "West Coast Haida Gwaii"
    covs: "-tv-depth-only"
    climate_mod: "2020-06-20-more2016"
    scrambled_years: FALSE
---

@@

# Calculate climate velocity
### Temperature
```{r}
rm(gf2)

# try({
#   gf2 <- readRDS(paste0("data/_climate_vocc/temp-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
# })

@@

# FULL DATASET
# mean(gf2$sd, na.rm = T) # [1] 0.3434
# min(gf2$sd, na.rm = T) # [1] 0.1266
# max(gf2$sd, na.rm = T) # [1] 1.12
# median(gf2$sd, na.rm = T) # [1] 0.287
# 
# 2008 DATASET
# values currently depend on survey region
temp_mean_sd <- mean(gf2$sd, na.rm = T) # [1] 0.3274
temp_mean_sd 
temp_median_sd <- median(gf2$sd, na.rm = T) # [1] 0.2882
temp_median_sd
temp_min_sd <- min(gf2$sd, na.rm = T) # [1] 0.1035
temp_min_sd*2
max(gf2$sd, na.rm = T) # [1] 1.248

# temp_sd_choice <- temp_min_sd*2
# temp_sd_choice <- temp_mean_sd
temp_sd_choice <- temp_median_sd

# lower_change_t <- temp_sd_choice
lower_change_t <- Inf
upper_change_t <- temp_sd_choice

rm(dvocc_t)

@@

saveRDS(gf2, file = paste0("data/_climate_vocc/temp-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
# saveRDS(gf2, file = paste0("data/_climate_vocc/temp-dvocc-min2SD-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
# saveRDS(gf2, file = paste0("data/_climate_vocc/temp-dvocc-medSDasy-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
}

# mean(gf2$sd, na.rm = T) # [1] 0.3274
temp_min_sd <- round(min(gf2$sd, na.rm = T), digits = 3) #

# temp_mean_sd <- mean(gf2$sd, na.rm = T) # 
# max(gf2$sd, na.rm = T) # [1] 1.248
temp_median_sd <- round(median(gf2$sd, na.rm = T), digits = 3) # [1] 0.2882
temp_mean_sd <- round(mean(gf2$sd, na.rm = T), digits = 3) #

print( paste("min SD =", round(temp_min_sd, digits = 2)))
print( paste("median SD =", round(temp_median_sd, digits = 2)))
print( paste("mean SD =", round(temp_mean_sd, digits = 2)))
print( paste("treshold chosen =", round(temp_mean_sd, digits = 2), "degrees C"))
```

```{r eval=F}
plot_vocc(gf2,
    raster_cell_size = 4,
  coast = TRUE,
  vec_aes = NULL,
  NA_label = "NA",
  fill_col = "dvocc",
  fill_label = "temperature \nkm/decade",
  raster_alpha = 1,
  na_colour = "white",
  mid_fill = "mistyrose1", grey_water = F,
  # mid_fill = "lavenderblush1", grey_water = F,
  low_fill = "royalblue4", # low_fill = "#5E4FA2",
  high_fill = "Red 3",
  raster_limits = c(0, 100),
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
    title = "distance-based temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year), " mean temp SD = ", signif(temp_mean_sd, digits = 2), " for min threshold of change")
)
```

@@

### Dissolved Oxygen
```{r }
rm(gf0)

try({
  gf0 <- readRDS(paste0("data/_climate_vocc/DO-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
})

@@

do_mean_sd <- mean(gf0$sd, na.rm = T)

do_min_sd
do_median_sd 
do_mean_sd

# do_sd_choice <- do_min_sd*2
do_sd_choice <- do_median_sd

lower_change_d <- c(do_sd_choice) 
upper_change_d <- c(do_sd_choice)

@@

lower_change_td <- c(Inf, do_sd_choice) 
upper_change_td <- c(temp_sd_choice, do_sd_choice)

@@

gf0 <- left_join(gf0, dv_td)
# 
saveRDS(gf0, file = paste0("data/_climate_vocc/DO-vocc-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
# saveRDS(gf0, file = paste0("data/_climate_vocc/DO-dvocc-min2SD-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
# saveRDS(gf0, file = paste0("data/_climate_vocc/DO-dvocc-meanSD-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
# saveRDS(gf0, file = paste0("data/_climate_vocc/DO-dvocc-medSD-", climate_mod, "-scale-", scale_fac, "-ssid", ssid_string, "-years-", years_sampled, ".rds"))
}

do_min_sd <- round(min(gf0$sd, na.rm = T), digits = 3)
do_mean_sd <- round(mean(gf0$sd, na.rm = T), digits = 3)
do_median_sd <- round(median(gf0$sd, na.rm = T), digits = 3)

print( paste("min SD =", do_min_sd))
print( paste("mean SD =", do_mean_sd))
print( paste("median SD =", do_median_sd))

do_sd_choice <- do_mean_sd
print( paste("treshold chosen =", signif(do_sd_choice, digits = 2), "ml/L"))

```{r eval=F}
plot_vocc(gf0,
    raster_cell_size = 4,
  coast = TRUE,
  vec_aes = NULL,
  NA_label = "NA",
  fill_col = "dvocc",
  fill_label = "km/decade",
  raster_alpha = 1,
  na_colour = "white",
  mid_fill = "honeydew", grey_water = F,
  # mid_fill = "lightyellow", grey_water = F,
  # mid_fill = "azure", grey_water = F,
  high_fill = "gold",
  low_fill = "darkcyan", # "lightseagreen",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
 title = "distance-based DO velocity",
  subtitle = paste0(min(d$year), "-", max(d$year), " DO SD = ", signif(do_sd_choice, 2), " for min threshold of DO change")
)
```

```{r eval=F}
plot_vocc(gf0,
    raster_cell_size = 4,
  coast = TRUE,
  vec_aes = NULL,
  NA_label = "NA",
  fill_col = "dvocc_both",
  fill_label = "km/decade",
  raster_alpha = 1,
  na_colour = "white",
  mid_fill = "honeydew", grey_water = F,
  # mid_fill = "lightyellow", grey_water = F,
  # mid_fill = "azure", grey_water = F,
  high_fill = "gold",
  low_fill = "darkcyan", # "lightseagreen",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
 title = "distance-based temp and DO velocity"
)
```
### BIOTIC VECTORS
```{r}
gf3 <- vocc_gradient_calc(d, "est",
  scale_fac = scale_fac,
  indices = indices,
  # divisor = 1, #default of 10 gives per decade
  log_space = TRUE,
  quantile_cutoff = 0.025
)

@@

```{r eval=T}
plot_vocc(vocc_t,
    raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "temp_dvocc",
  fill_label = "temperature \nkm/decade",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
   # viridis_option = "C",
   mid_fill = "lightyellow",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
    title = "distance-based temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year), " min temp SD = ", temp_mean_sd, " for 95% min threshold of change")
)
```
